### 2015-06-01 Dissertation/chapter-graybox.tex
fitness improving -> fitness-improving

\section{Efficient Local Search}
\label{sec-whitley-ls}
Section~\ref{sec-hill-climber} presented an efficient method for performing local search for the black-box
domain. Each potential bit flip, referred to here as a move, requires the entire solution to be reevaluated, which takes $\Omega(N)$ time.
Furthermore, each time a fitness improving move is made all previously tested moves must be tested again. As a result
improving a random solution to be a local optimum using this algorithm requires between $\Omega(N^2)$ and \BigO{IN^2}, where $I$ is the number
of improving moves. The lower bound is achieved when the while loop in Figure~\ref{fig-hc} runs a constant number of times.
For instance on One Max, Deceptive Trap, Deceptive Step Trap, and HIFF all possible single bit improvements are found during
the first time through the loop. The worst case is when each loop is expected to only make a single improving move, which causes
all $N$ moves to be reevaluated once per improvement, such as on the Leading Ones problem.

@@

When performing hill climbing, only moves $m$ such that $delta[m] > 0$ are fitness improving moves. Initially
all moves are considered $open$, meaning that they could potentially be fitness improvements. Each iteration
a random move $m$ is chosen from $open$, and $delta[m]$ is checked. If $m$ is a fitness improving move,
\Call{MakeMove}{$m$}, shown in Figure~\ref{fig-make-move}, is called.

@@

\Call{MakeMove}{} updates the fitness and $delta$ values to reflect the change in the solution. The fitness
of the solution after making the move does not require any calls to $f_s$ as $delta[m]$ already stores the
change in fitness. This process requires updating all of the $delta$ values for the $k$ moves that interact with each of the $c$ subfunctions
effected by $m$. This update replaces outdated information that used the original solution ($just\_m' - pre\_both$)
with how much the move improves over the new solution ($post\_both - just\_m$). As $delta[m']$ has updated, $m'$ could
potentially become a fitness improving move and is therefore added into $open$. As $m$ was just flipped,
it cannot be a fitness improvement and is therefore removed from $open$.  In total this requires less than
$ck4b(k)$ time, which is \BigO{1} assuming $c$, $k$, and $b(k)$ do not scale with $N$.

>>>>

\section{Efficient Local Search}
\label{sec-whitley-ls}
Section~\ref{sec-hill-climber} presented an efficient method for performing local search for the black-box
domain. Each potential bit flip, referred to here as a move, requires the entire solution to be reevaluated, which takes $\Omega(N)$ time.
Furthermore, each time a fitness-improving move is made all previously tested moves must be tested again. As a result
improving a random solution to be a local optimum using this algorithm requires between $\Omega(N^2)$ and \BigO{IN^2}, where $I$ is the number
of improving moves. The lower bound is achieved when the while loop in Figure~\ref{fig-hc} runs a constant number of times.
For instance on One Max, Deceptive Trap, Deceptive Step Trap, and HIFF all possible single bit improvements are found during
the first time through the loop. The worst case is when each loop is expected to only make a single improving move, which causes
all $N$ moves to be reevaluated once per improvement, such as on the Leading Ones problem.

@@

When performing hill climbing, only moves $m$ such that $delta[m] > 0$ are fitness-improving moves. Initially
all moves are considered $open$, meaning that they could potentially be fitness improvements. Each iteration
a random move $m$ is chosen from $open$, and $delta[m]$ is checked. If $m$ is a fitness-improving move,
\Call{MakeMove}{$m$}, shown in Figure~\ref{fig-make-move}, is called.

@@

\Call{MakeMove}{} updates the fitness and $delta$ values to reflect the change in the solution. The fitness
of the solution after making the move does not require any calls to $f_s$ as $delta[m]$ already stores the
change in fitness. This process requires updating all of the $delta$ values for the $k$ moves that interact with each of the $c$ subfunctions
effected by $m$. This update replaces outdated information that used the original solution ($just\_m' - pre\_both$)
with how much the move improves over the new solution ($post\_both - just\_m$). As $delta[m']$ has updated, $m'$ could
potentially become a fitness-improving move and is therefore added into $open$. As $m$ was just flipped,
it cannot be a fitness improvement and is therefore removed from $open$.  In total this requires less than
$ck4b(k)$ time, which is \BigO{1} assuming $c$, $k$, and $b(k)$ do not scale with $N$.

### 2015-06-01 Dissertation/chapter-internal.tex
fitness improving -> fitness-improving

\begin{figure}[t]
  \begin{centering}
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{cross}
      \end{centering}
      \caption{Crossover Proportion}
      \label{fig-cross}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{cross-success}
      \end{centering}
      \caption{Crossover Success}
      \label{fig-cross-success}
    \end{subfigure}
  \end{centering}
  \caption{For each problem Figure~\ref{fig-cross} shows the proportion of P3 evaluations spend on crossovers
           and Figure~\ref{fig-cross-success} shows the percentage of fitness improving crossover evaluations.}
\end{figure}

@@

\subsection{Pyramid}
\begin{figure}[t]
  \begin{centering}
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{level-size}
      \end{centering}
      \caption{Population Size}
      \label{fig-level-size}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{level-success}
      \end{centering}
      \caption{Crossover Success}
      \label{fig-level-success}
    \end{subfigure}
  \end{centering}
  \caption{For each problem Figure~\ref{fig-level-size} shows the number of solutions stored in each level of the pyramid
           and Figure~\ref{fig-level-success} shows the percentage of fitness improving crossover evaluations at each level.}
\end{figure}

>>>>

\begin{figure}[t]
  \begin{centering}
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{cross}
      \end{centering}
      \caption{Crossover Proportion}
      \label{fig-cross}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{cross-success}
      \end{centering}
      \caption{Crossover Success}
      \label{fig-cross-success}
    \end{subfigure}
  \end{centering}
  \caption{For each problem Figure~\ref{fig-cross} shows the proportion of P3 evaluations spend on crossovers
           and Figure~\ref{fig-cross-success} shows the percentage of fitness-improving crossover evaluations.}
\end{figure}

@@

\subsection{Pyramid}
\begin{figure}[t]
  \begin{centering}
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{level-size}
      \end{centering}
      \caption{Population Size}
      \label{fig-level-size}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{level-success}
      \end{centering}
      \caption{Crossover Success}
      \label{fig-level-success}
    \end{subfigure}
  \end{centering}
  \caption{For each problem Figure~\ref{fig-level-size} shows the number of solutions stored in each level of the pyramid
           and Figure~\ref{fig-level-success} shows the percentage of fitness-improving crossover evaluations at each level.}
\end{figure}
